
\documentclass[11pt, letterpaper]{article}
% Ensure that generate pdf is machine readable/ATS parsable:
\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    \usepackage[T1]{fontenc}
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi

% package for setting margins
\usepackage [
ignoreheadfoot, 
left=0.4in, right=0.4in, top=0.2in, bottom=0in]{geometry}
% icons package
\usepackage{fontawesome5}
% ordered list
\usepackage{enumitem}
% to format hyperlinks
\usepackage{hyperref}
% Required for ifthenelse statements
\usepackage{xifthen} 
% package to set 0 margin for paragraph, so no pre-defined indent
\usepackage[parfill]{parskip}
% package for tabular content
\usepackage{tabularx}
% used to set proper left margins for items.
\setlist[itemize]{leftmargin=4.6mm}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}
% Save the original \href command in a new command
\let\hrefWithoutArrow\href

% Optionally redefine \hrefWithoutArrow to customize it
% For example, redefine it to not show the arrow:
\renewcommand{\hrefWithoutArrow}[2]{%
    \href{#1}{#2}%
}

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

% for each section heading

\newcommand{\sectionHeading}[1]{
    \MakeUppercase{\textbf{#1}}
    \vspace{4pt}
    \hrule{}
    \vspace{-2pt}
}

\newcommand{\resumeSubheading}[4]{
    \noindent % Prevent indentation
    \ifthenelse{\isempty{#1}}%
        {}% if #1 is empty
        {\begin{tabularx}{\textwidth}{@{}X@{\hspace{10pt}}r@{}}
            \large{\textbf{#1}} & #2 \\
        \end{tabularx}}
    \ifthenelse{\isempty{#3}}%
        {}% if #1 is empty
        {\begin{tabularx}{\textwidth}{@{}X@{\hspace{10pt}}r@{}}
            #3 & \Small{\textit{#4}} \\
        \end{tabularx}}
}

\newcommand{\resumeSubsection}[4]{
    \noindent % Prevent indentation
    \ifthenelse{\isempty{#1}}%
        {\vspace{-10pt}}% if #1 is empty
        {\begin{tabularx}{\textwidth}{@{}X@{\hspace{10pt}}r@{}}
            \large{\textbf{#1}} & #2 \\
        \end{tabularx}}
    \ifthenelse{\isempty{#3}}%
        {\vspace{-10pt}}% if #1 is empty
        {\begin{tabularx}{\textwidth}{@{}X@{\hspace{10pt}}r@{}}
            #3 & #4 \\
        \end{tabularx}}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubsection}[2]{
    \noindent % Prevent indentation
    \ifthenelse{\isempty{#1}}%
        {\vspace{-22pt}}% if #1 is empty
        {\begin{tabularx}{\textwidth}{@{}X@{\hspace{10pt}}r@{}}
            \large{\textbf{#1}} & #2 \\
        \end{tabularx}}
}




\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}

\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeDescription}[1]{
    \textit{#1}
}


\begin{document}
\begin{center}
\textbf{\Huge \scshape Aditya Gandhi }
\end{center}

\begin{center}
\vspace{5pt}
\faEnvelopeSquare \hspace{5pt} {\href{mailto:csdc}{csdc}}  
\hspace{2pt} \textbar{} \hspace{2pt} \faPhone \hspace{5pt} 6787494902  
\hspace{2pt} \textbar{} \hspace{2pt}\faLaptopCode \hspace{5pt} {\href{adityagandhi.netlify.app}{adityagandhi.netlify.app}} 
\hspace{2pt} \textbar{} \hspace{2pt}\faLinkedinIn \hspace{5pt} {\href{linkedin.com/asasxasxas}{linkedin.com/asasxasxas}} 
\hspace{2pt} \textbar{} \hspace{2pt}\faInstagram \hspace{5pt} {\href{insta.com/adcbhbhcs}{insta.com/adcbhbhcs}} 
\hspace{2pt} \textbar{} \hspace{2pt}\faFacebook \hspace{5pt} {\href{fb kon rakhe}{fb kon rakhe}} 
\hspace{2pt} \textbar{} \hspace{2pt}\faGithub \hspace{5pt} {\href{github.com/asdasdf}{github.com/asdasdf}} 
\hspace{2pt} \textbar{} \hspace{2pt}\faAddressBook  \hspace{5pt} kyay pan pahch 
\hspace{2pt} \textbar{} \hspace{2pt}\faDiagnoses  \hspace{5pt} koi pan role  \vspace{4pt} summary has to be of one line only. prepare accordingly. 
\end{center}

\sectionHeading{Objective}
\setlength{\leftmargin}{0em}
\resumeDescription{My main objective in life is to complete this resume \textit{maker project for now. Learn} more back-end}

% EDUCATION SECTION
\sectionHeading{Education}
\setlength{\leftmargin}{0em}
\resumeSubheading{\textbf{georgia-Tech}}{Aug 2023 \textbf{- Aug 2025}}{masters \textit{in com}piter science}{\underline{3.86 / 4.00}}
\begin{itemize}
\vspace{-6pt}
\item \hspace{-2.5pt} There are not many features associated wt Gatech.
\vspace{-6pt}
\item \hspace{-2.5pt} Now there is some more \textit{content a}s well
\vspace{-6pt}
\item \hspace{-2.5pt} I am jsut dofing this to check spacing\end{itemize}

\setlength{\leftmargin}{0em}
\resumeSubheading{Pandit Deendayal Energy Institute - PDEU}{Aug 2019 - May 2023}{Bachelors of technology}{9.86 / 10.00}

% WORK EXPERIENCE SECTION
\sectionHeading{Work Experience}
\setlength{\leftmargin}{0em}\resumeSubsection{Cling Multi-Solutions}{January 2023 - June 2023}{SDE Intern}{Pune, Maharashtra}
\begin{itemize}
\vspace{-6pt}
\item \hspace{-2.5pt} work-str1. ho hasnt. tell mah.\end{itemize}

\setlength{\leftmargin}{0em}\resumeSubsection{eInfoChips org}{May 2022 - July 2022}{Summer Intern}{Remote}

% PROJECTS
\sectionHeading{Projects}
\setlength{\leftmargin}{0em}
\resumeSubsection{Portfolio Website | ReactJS, Framer-Motion, ts Particles, Three.js, JavaScript, SCSS}{}{}{}
\begin{itemize}
\vspace{-6pt}
\item \hspace{-2.5pt} Constructed a personalized portfolio website through ReactJS framework. Deployed tsParticles.js library for an interactive background, leading to 40 increase in user interactions. • Employed animations through Framer-motion library for elevated user view-ability. • Incorporated custom 3D objects using the Three.js library to demonstrate advanced web development skills.3\end{itemize}

\setlength{\leftmargin}{0em}
\resumeSubsection{B+ Tree Implementation | C++}{}{}{}
\begin{itemize}
\vspace{-6pt}
\item \hspace{-2.5pt} Engineered a B+-Tree from scratch, supporting lookup, insert and delete operations. • Designed it as a template, allowing custom key and value types, comparators and page size at compile time. • Leverages page-ids and buffer-manager instead of pointers for node resolution, for faster data retrieval and management. Implemented node splitting and merging logic for refined balance in the tree.\end{itemize}


% CERTIFICATES
\sectionHeading{Certificates}
\setlength{\leftmargin}{0em}
\resumeSubSubsection{Leetcode Guardian badge achieved}{}
\begin{itemize}
\vspace{-6pt}
\item \hspace{-2.5pt} ReactJS, NextJS, Framer Motion, Three.js, Bootstrap, Tailwind, Django, Tensorflow, Numpy, Keras\end{itemize}

\setlength{\leftmargin}{0em}
\resumeSubSubsection{Management Head at HackerEarth PDEU Student Chapter}{}
\begin{itemize}
\vspace{-6pt}
\item \hspace{-2.5pt} ReactJS, NextJS, Framer Motion, Three.js, Bootstrap, Tailwind, Django, Tensorflow, Numpy, Keras\end{itemize}


% SKILLS
\sectionHeading{Skills}
\setlength{\leftmargin}{0em}
\resumeSubSubsection{technical skills}{}
\begin{itemize}
\vspace{-6pt}
\item \hspace{-2.5pt} ReactJS, NextJS, Framer Motion, Three.js, Bootstrap, Tailwind, Django, Tensorflow, Numpy, Keras\end{itemize}

\setlength{\leftmargin}{0em}
\resumeSubSubsection{Libraries}{}
\begin{itemize}
\vspace{-6pt}
\item \hspace{-2.5pt} ReactJS, NextJS, Framer Motion, Three.js, Bootstrap, Tailwind, Django, Tensorflow, Numpy, Keras\end{itemize}


% LANGUAGES
\sectionHeading{Languages}
\setlength{\leftmargin}{0em}
\resumeSubSubsection{English}{}
\begin{itemize}
\vspace{-6pt}
\item \hspace{-2.5pt} I mastered English during my GRE prep. I also scored 8 bands in IELTS\end{itemize}

\setlength{\leftmargin}{0em}
\resumeSubSubsection{Gujarati}{}
\begin{itemize}
\vspace{-6pt}
\item \hspace{-2.5pt} I have good command over Gujarati and consider it my native language.\end{itemize}

\end{document}
                